--- 
title: "Data Science from Scratch Code"
author: "Joffrey Anthony"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
---

# Computer Set-Up

When building projects *efficiently*, you will need different set-ups in order to have everything in your code work properly, *not only on your own machine, but also on other machines, for example of another team-member*.

## Virtual Environment 

Because the libraries you work with in your projects will be updated over time (this is generally *bad news*, since this will cause all sorts of dependency problems across your libaries you use), it is crucial to understand that you will need a virtual environment (`venv`). There, you will install all the libraries you need. The **major advantage here, is that you can control the version you install the library**. Furthermore, you can send the `venv` to another computer and the people will download exactly the versions of each library. 

<mark>This allows that **your code will <u>always</u> work, independently of the machine you will use**! There will be no dependency problems anymore, which is a huge win.</mark>. :)

### Create a `venv`

Go to your terminal and plug in the following code:

```{terminal}
conda create -n YOUR-VENVIRONMENT-NAME-HERE python=3.6
```

### Activate your newly created `venv`

Weirdly though, you also need to activate the environment you created above. Plug in the following code:

```{terminal}
source activate YOUR-ENVIRONMENT-NAME
```

<mark>**Note that the code above can also be used to activate virtual environments you created in the past**!</mark> =) 

# R Markdown

When writing Code, I recommend you to use `.Rmd`-Documents, which will allow you to combine both, text, as well as Code (in R, Python, or any other language of your choice).

Actually, this document is written in `.Rmd`-Files, where I combine the text, with so-called "code-snippets", like the follwing:

```{text}
This is a Code-Snippet
```

When writing Code in `R-Markdown`, it will be useful for you to know when: 

1) to execute code wihtin a code-snippet
2) and where not.

## Hide Source Code

This will be done with `echo = FALSE`:

```{r, echo=FALSE}
1 + 1
```

With figures, you need `fig.show = 'hide'` in R:

```{r, fig.show='hide'}
plot(cars)
```

To hide warning-messages, just use `message = FALSE`:

```{r, message=FALSE}
message("You will not see the message.")
```

## Execute a Code-Chunk without showing any Output

You will get an output, e.g. the code will execute, but you will not show the code.

```{r, include=FALSE}
# any R code here
```

## Do NOT execute a Code-Chunk

If you want to show code for demonstration purposes - like on this Website - 
you will probably want to only show the code, but not execute it. This is also possible with `eval=FALSE`:

```{r, include=FALSE}
# any R code here
```


